### 2014-10-30 thesis/appendix/tr-corr-threshold-features.tex
Complete all results tables for the trauma data set

\begin{table}[htbp]
\caption{}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Pearson Correlation - Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 57 & 73.08\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson, gcs, triss, bp, age, chest3, anypelvis, head3, headminor, mentalhealth, rr, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3, upper\_limbop, externalany, english \\ \hline
0.01 & 54 & 69.23\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson, gcs, triss, bp, age, chest3, anypelvis, head3, headminor, mentalhealth, rr, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3 \\ \hline
0.05 & 41 & 52.56\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson, gcs, triss, bp, age, chest3, anypelvis, head3, headminor, mentalhealth, rr, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, faceany, any\_heart, any\_cancer, face3, upperlimboponly \\ \hline
0.1 & 29 & 37.18\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson, gcs, triss, bp, age, chest3, anypelvis, head3, headminor, mentalhealth, rr, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface \\ \hline
0.125 & 20 & 25.64\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson, gcs, triss, bp, age, chest3, anypelvis, head3, headminor \\ \hline
0.15 & 12 & 15.38\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson \\ \hline
0.2 & 7 & 8.97\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3 \\ \hline
0.3 & 1 & 1.28\% & traumatier \\ \hline
0.5 & 0 & 0.00\% & - \\ \hline
0.75 & 0 & 0.00\% & - \\ \hline
\end{tabular}}
\end{table}

\begin{table}[htbp]
\caption{}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{11cm}|}
\hline
\multicolumn{ 4}{|c|}{Pearson Correlation - No discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 58 & 74.36\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery, chest3, anypelvis, headminor, head3, mentalhealth, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, rr, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, pr, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, bp, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3, upper\_limbop, externalany, english \\ \hline
0.01 & 55 & 70.51\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery, chest3, anypelvis, headminor, head3, mentalhealth, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, rr, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, pr, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, bp, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3 \\ \hline
0.05 & 41 & 52.56\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery, chest3, anypelvis, headminor, head3, mentalhealth, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, rr, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, pr, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, bp, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3 \\ \hline
0.1 & 27 & 34.62\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery, chest3, anypelvis, headminor, head3, mentalhealth, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, rr, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, pr, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, bp, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3 \\ \hline
0.125 & 19 & 24.36\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery, chest3, anypelvis, headminor, head3, mentalhealth, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, rr, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, pr, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, bp, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3 \\ \hline
0.15 & 15 & 19.23\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery \\ \hline
0.2 & 9 & 11.54\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss \\ \hline
0.3 & 2 & 2.56\% & iss, traumatier \\ \hline
0.5 & 0 & 0.00\% & - \\ \hline
0.75 & 0 & 0.00\% & - \\ \hline
\end{tabular}}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Features selected from the discretised trauma data set using varying thresholds of Pearson's correlation coefficient. Features shown are in order from highest to lowest correlation with the class.}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Pearson Correlation - Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 57 & 73.08\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson, gcs, triss, bp, age, chest3, anypelvis, head3, headminor, mentalhealth, rr, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3, upper\_limbop, externalany, english \\ \hline
0.01 & 54 & 69.23\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson, gcs, triss, bp, age, chest3, anypelvis, head3, headminor, mentalhealth, rr, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3 \\ \hline
0.05 & 41 & 52.56\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson, gcs, triss, bp, age, chest3, anypelvis, head3, headminor, mentalhealth, rr, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, faceany, any\_heart, any\_cancer, face3, upperlimboponly \\ \hline
0.1 & 29 & 37.18\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson, gcs, triss, bp, age, chest3, anypelvis, head3, headminor, mentalhealth, rr, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface \\ \hline
0.125 & 20 & 25.64\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson, gcs, triss, bp, age, chest3, anypelvis, head3, headminor \\ \hline
0.15 & 12 & 15.38\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3, bodyregions, operation, lowerlimbnopelvis, neurosurgery, charlson \\ \hline
0.2 & 7 & 8.97\% & traumatier, icu, iss, upperlimbonly, lower\_limbop, lowerlimbany, lower3 \\ \hline
0.3 & 1 & 1.28\% & traumatier \\ \hline
0.5 & 0 & 0.00\% & - \\ \hline
0.75 & 0 & 0.00\% & - \\ \hline
\end{tabular}}
\end{table}

\begin{table}[htbp]
\caption{Features selected from the non-discretised trauma data set using varying thresholds of Pearson's correlation coefficient. Features shown are in order from highest to lowest correlation with the class.}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{11cm}|}
\hline
\multicolumn{ 4}{|c|}{Pearson Correlation - No discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 58 & 74.36\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery, chest3, anypelvis, headminor, head3, mentalhealth, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, rr, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, pr, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, bp, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3, upper\_limbop, externalany, english \\ \hline
0.01 & 55 & 70.51\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery, chest3, anypelvis, headminor, head3, mentalhealth, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, rr, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, pr, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, bp, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3 \\ \hline
0.05 & 41 & 52.56\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery, chest3, anypelvis, headminor, head3, mentalhealth, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, rr, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, pr, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, bp, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3 \\ \hline
0.1 & 27 & 34.62\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery, chest3, anypelvis, headminor, head3, mentalhealth, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, rr, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, pr, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, bp, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3 \\ \hline
0.125 & 19 & 24.36\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery, chest3, anypelvis, headminor, head3, mentalhealth, normalvitals, arrivalmode, spine3, headany, laparotomy, spineany, headface, chestany, rr, abdo3, penetrating, abdoany, any\_stroketia, mechcode, any\_dm, pr, faceany, any\_heart, any\_cancer, face3, upperlimboponly, any\_liver, any\_kidney, thoracotomy, bp, married, upperlimbany, pelvic\_fracture, ext3, alcohol, sex, neckany, upper3, transfer, neck3 \\ \hline
0.15 & 15 & 19.23\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss, charlson, age, gcs, operation, lowerlimbnopelvis, neurosurgery \\ \hline
0.2 & 9 & 11.54\% & iss, traumatier, icu, upperlimbonly, bodyregions, lower\_limbop, lowerlimbany, lower3, triss \\ \hline
0.3 & 2 & 2.56\% & iss, traumatier \\ \hline
0.5 & 0 & 0.00\% & - \\ \hline
0.75 & 0 & 0.00\% & - \\ \hline
\end{tabular}}
\end{table}

### 2014-10-30 thesis/appendix/tr-ig-threshold-features.tex
Complete all results tables for the trauma data set

\begin{table}[htbp]
\caption{}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Information Gain - Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 57 & 73.08\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, rr, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, any\_cancer, any\_dm, any\_heart, faceany, face3, upperlimboponly, any\_kidney, thoracotomy, any\_liver, married, pelvic\_fracture, upperlimbany, ext3, alcohol, sex, neckany, upper3, transfer, neck3, upper\_limbop, externalany, english \\ \hline
0.001 & 47 & 60.26\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, rr, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, any\_cancer, any\_dm, any\_heart, faceany, face3, upperlimboponly, any\_kidney, thoracotomy, any\_liver, married, pelvic\_fracture, upperlimbany \\ \hline
0.005 & 33 & 42.31\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, rr, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating \\ \hline
0.01 & 27 & 34.62\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, rr, mentalhealth, spine3, normalvitals \\ \hline
0.05 & 4 & 5.13\% & iss, triss, traumatier, icu \\ \hline
0.1 & 2 & 2.56\% & iss, triss \\ \hline
0.15 & 1 & 1.28\% & iss \\ \hline
0.2 & 0 & 0.00\% &  \\ \hline
0.3 & 0 & 0.00\% &  \\ \hline
0.5 & 0 & 0.00\% &  \\ \hline
\end{tabular}}
\end{table}

\begin{table}[htbp]
\caption{}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Information Gain - No discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 57 & 73.08\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, rr, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, any\_cancer, any\_dm, any\_heart, faceany, face3, upperlimboponly, any\_kidney, thoracotomy, any\_liver, married, pelvic\_fracture, upperlimbany, ext3, alcohol, sex, neckany, upper3, transfer, neck3, upper\_limbop, externalany, english \\ \hline
0.001 & 47 & 60.26\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, rr, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, any\_cancer, any\_dm, any\_heart, faceany, face3, upperlimboponly, any\_kidney, thoracotomy, any\_liver, married, pelvic\_fracture, upperlimbany \\ \hline
0.005 & 33 & 42.31\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, rr, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating \\ \hline
0.01 & 27 & 34.62\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, rr, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, mentalhealth, spine3, normalvitals \\ \hline
0.05 & 5 & 6.41\% & iss, triss, traumatier, icu, bodyregions \\ \hline
0.1 & 2 & 2.56\% & iss, triss \\ \hline
0.15 & 1 & 1.28\% & iss \\ \hline
0.2 & 0 & 0.00\% &  \\ \hline
0.3 & 0 & 0.00\% &  \\ \hline
0.5 & 0 & 0.00\% &  \\ \hline
\end{tabular}}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Features selected from the discretised trauma data set at varying thresholds of information gain. Features shown are in order from highest to lowest information gain.}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Information Gain - Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 57 & 73.08\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, rr, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, any\_cancer, any\_dm, any\_heart, faceany, face3, upperlimboponly, any\_kidney, thoracotomy, any\_liver, married, pelvic\_fracture, upperlimbany, ext3, alcohol, sex, neckany, upper3, transfer, neck3, upper\_limbop, externalany, english \\ \hline
0.001 & 47 & 60.26\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, rr, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, any\_cancer, any\_dm, any\_heart, faceany, face3, upperlimboponly, any\_kidney, thoracotomy, any\_liver, married, pelvic\_fracture, upperlimbany \\ \hline
0.005 & 33 & 42.31\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, rr, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating \\ \hline
0.01 & 27 & 34.62\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, rr, mentalhealth, spine3, normalvitals \\ \hline
0.05 & 4 & 5.13\% & iss, triss, traumatier, icu \\ \hline
0.1 & 2 & 2.56\% & iss, triss \\ \hline
0.15 & 1 & 1.28\% & iss \\ \hline
0.2 & 0 & 0.00\% & - \\ \hline
0.3 & 0 & 0.00\% & - \\ \hline
0.5 & 0 & 0.00\% & - \\ \hline
\end{tabular}}
\end{table}

\begin{table}[htbp]
\caption{Features selected from the non-discretised trauma data set at varying thresholds of information gain. Features shown are in order from highest to lowest information gain.}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Information Gain - No discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 57 & 73.08\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, rr, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, any\_cancer, any\_dm, any\_heart, faceany, face3, upperlimboponly, any\_kidney, thoracotomy, any\_liver, married, pelvic\_fracture, upperlimbany, ext3, alcohol, sex, neckany, upper3, transfer, neck3, upper\_limbop, externalany, english \\ \hline
0.001 & 47 & 60.26\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, rr, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating, abdoany, any\_stroketia, any\_cancer, any\_dm, any\_heart, faceany, face3, upperlimboponly, any\_kidney, thoracotomy, any\_liver, married, pelvic\_fracture, upperlimbany \\ \hline
0.005 & 33 & 42.31\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, rr, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, mentalhealth, spine3, normalvitals, spineany, headany, headface, chestany, abdo3, penetrating \\ \hline
0.01 & 27 & 34.62\% & iss, triss, traumatier, icu, bodyregions, arrivalmode, lower\_limbop, lower3, upperlimbonly, lowerlimbany, charlson, age, gcs, mechcode, neurosurgery, operation, rr, lowerlimbnopelvis, bp, anypelvis, chest3, head3, headminor, laparotomy, mentalhealth, spine3, normalvitals \\ \hline
0.05 & 5 & 6.41\% & iss, triss, traumatier, icu, bodyregions \\ \hline
0.1 & 2 & 2.56\% & iss, triss \\ \hline
0.15 & 1 & 1.28\% & iss \\ \hline
0.2 & 0 & 0.00\% & -  \\ \hline
0.3 & 0 & 0.00\% & - \\ \hline
0.5 & 0 & 0.00\% & - \\ \hline
\end{tabular}}
\end{table}

### 2014-10-30 thesis/appendix/tr-nothreshold-features.tex
Complete all results tables for the trauma data set

\begin{table}[hbp]
\caption{}
\begin{tabular}{|l|r|r|p{8.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Discretisation} \\ \hline
Method & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
CFS & 9 & 11.54\% & icu, iss, traumatier, bodyregions, lower3, lower\_limbop, triss, upperlimbonly, any\_cancer \\ \hline
C4.5 Wrapper & 11 & 14.10\% & age, bp, icu, iss, faceany, lowerlimbany, ext3, operation, upperlimboponly, lowerlimbnopelvis, any\_cancer \\ \hline
Baseline & 19 & 24.36\% & normalvitals, gcs1, iss8, age65, penetrating, headany, chestany, abdoany, spineany, upperlimbany, lowerlimbany, mentalhealth, operation, anymedical, mva, mba, pedestrian, fallsonly, cyclist \\ \hline
Expert Selection & 11 & 14.10\% & age, normalvitals, gcs1, icu1, iss, transfer, mechcode, upperlimbany, lowerlimbany, head3, charlson \\ \hline
\end{tabular}
\vspace{1cm}
\vfill
\begin{tabular}{|l|r|r|p{8.5cm}|}
\hline
\multicolumn{ 4}{|c|}{No discretisation} \\ \hline
Method & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
CFS & 9 & 11.54\% & icu, iss, traumatier, bodyregions, lower3, lower\_limbop, triss, upperlimbonly, any\_cancer \\ \hline
C4.5 Wrapper & 10 & 12.82\% & gcs, iss, abdo3, ext3, laparotomy, upper\_limbop, lower\_limbop, charlson, triss, any\_kidney \\ \hline
Baseline & 19 & 24.36\% & normalvitals, gcs1, iss8, age65, penetrating, headany, chestany, abdoany, spineany, upperlimbany, lowerlimbany, mentalhealth, operation, anymedical, mva, mba, pedestrian, fallsonly, cyclist \\ \hline
Expert Selection & 11 & 14.10\% & age, normalvitals, gcs1, icu1, iss, transfer, mechcode, upperlimbany, lowerlimbany, head3, charlson \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[hbp]
\caption{Features selected using automatic methods which select the best subset and do not require a threshold (CFS and C4.5 wrapper), as well as using the manual methods: the features recommended by the domain expert and the baseline feature set from Dinh et. al. Features are not ranked with these feature selectors.}
\begin{tabular}{|l|r|r|p{8.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Discretisation} \\ \hline
Method & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
CFS & 9 & 11.54\% & icu, iss, traumatier, bodyregions, lower3, lower\_limbop, triss, upperlimbonly, any\_cancer \\ \hline
C4.5 Wrapper & 11 & 14.10\% & age, bp, icu, iss, faceany, lowerlimbany, ext3, operation, upperlimboponly, lowerlimbnopelvis, any\_cancer \\ \hline
Baseline & 19 & 24.36\% & normalvitals, gcs1, iss8, age65, penetrating, headany, chestany, abdoany, spineany, upperlimbany, lowerlimbany, mentalhealth, operation, anymedical, mva, mba, pedestrian, fallsonly, cyclist \\ \hline
Expert Selection & 11 & 14.10\% & age, normalvitals, gcs1, icu1, iss, transfer, mechcode, upperlimbany, lowerlimbany, head3, charlson \\ \hline
\end{tabular}
\vspace{1cm}
\vfill
\begin{tabular}{|l|r|r|p{8.5cm}|}
\hline
\multicolumn{ 4}{|c|}{No discretisation} \\ \hline
Method & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
CFS & 9 & 11.54\% & icu, iss, traumatier, bodyregions, lower3, lower\_limbop, triss, upperlimbonly, any\_cancer \\ \hline
C4.5 Wrapper & 10 & 12.82\% & gcs, iss, abdo3, ext3, laparotomy, upper\_limbop, lower\_limbop, charlson, triss, any\_kidney \\ \hline
Baseline & 19 & 24.36\% & normalvitals, gcs1, iss8, age65, penetrating, headany, chestany, abdoany, spineany, upperlimbany, lowerlimbany, mentalhealth, operation, anymedical, mva, mba, pedestrian, fallsonly, cyclist \\ \hline
Expert Selection & 11 & 14.10\% & age, normalvitals, gcs1, icu1, iss, transfer, mechcode, upperlimbany, lowerlimbany, head3, charlson \\ \hline
\end{tabular}
\end{table}
